Type Error Telemetry at Scale

### 2023-09-23 programming23/paper.tex
more related work

\begin{table}[t]\centering
  \caption{Comparing telemetry systems}
  \label{t:telemetry-design}

@@

The BlackBox project similarly collects telemetry in broad strokes.
Every Java program submitted for compilation goes into the BlackBox database (minus
any comments above the main class) along with the compiler's response~\cite{bkmu-sigcse-2014}.
Though somewhat intrusive, the millions of programs in the BlackBox dataset
have enabled dozens of contributions to the area of CS
education~\cite{bask-icer-2018}, ranging from categorization of novice
errors~\cite{mk-fie-2014,m-masters-2016} to analyses of error frequency and
time-to-fix~\cite{ab-sigcse-2015}.

@@

One way to futher strengthen the privacy of any telemetry design, including
transparent telemetry, is to fuzz the data using techniques from
differential privacy~\cite{zhlbr-cc-2020,epk-ccs-2014,wblj-usenix-2017}.
Recent work on fuzzing traces~\cite{zhlbr-cc-2020},
accounting for known relationships between events~\cite{zhlbr-oopsla-2020},
and performing the fuzzing on the client side~\cite{hlzbr-ecoop-2021} is
especially relevant to the session-based data that Roblox Studio collects.
Applying differential privacy is subtle, however.
While we can likely fuzz the total number of type errors, if we were to
fuzz the number of \code{CodeTooComplex} errors carelessly, it might drastically
affect our conclusions.

Lastly, cooperative bug isolation is a related method for designing
telemetry systems~\cite{liblit-thesis}.
%% \FILL{} adaptive bug isolation~\cite{nl-icse-2010}, search on the control dependence graph.
%% 1\% overhead vs 87\% for sampling and 300\% for binary instrumentation
The focus is not on privacy, but rather on how to collect a small amount of
data from each user and perform statistically-sound analyses.
Each feature of interest \emph{within} a user's codebase has a uniform-random
probability of contributing telemetry.
The system-builder can analyze this telemetry with predicates to identify
notable events and logistic regression to narrow down nondeterministic bugs.
There is a high burden on designers to decide what to capture,
but a careful design can minimize the data from each individual user.
%% more in diss: how to deal with native compilers, threads, dynamic loading
%% ... privacy is future work, can maybe avoid private data with a type system

\paragraph{Telemetry Rates}

We chose randomly, uniform distribution.

\cite{lnsmc-usenix-2018} blame-proportional logging,
scale up ``near'' points of interest,
could be useful for us in the future.
\cite{fnm-sigmod-2020} ditto, faster than statistical at finding root-cause,
deterministic.

RAMSS workshop series.

%% - zfstt-ieeesensors-2022
%% - lit review, benefits of static types
%%   http://danluu.com/empirical-pl/
%% - thomas kennedy .... generic usage monitoring ascilite 2003
%% - ahmadzadeh elliman higgins iticse 2005
%% - buffardi etal 2014 adaptive and social mechanisms
%% - bddf-icse-2016
%% -  sh edwards and jason snyder icer 2009 comparing effective and ineffective grading platform
%% - murphy etal sigcse 2009 Retina: helping students
%% - ESP workshop on empirical studies of programming
%%   https://dl.acm.org/doi/proceedings/10.1145/266399
%%   nothing sounds big ... empirical yes, large no
%% - Choppella Haynes IU TR 426
%% - Tip Dinesh tosem 2001

\paragraph{Contrast: User Studies and Types and/or Proofs}

@@

\paragraph{Errors}

- - -

\cite{wk-koli-2020,lgk-pj-2022} 
even more edit sequences
b2t2, examplar, ... must be others outside brown!!

@@

\newpage

\appendix

\section{Data Details}

Tips for interpreting the data:

\begin{itemize}
  \item
    Edit ranges are non-negative because we
    implemented the interval arithmetic for them using unsigned integers.
    To filter out negative edit ranges, we removed all ranges
    greater than 4 billion.

  \item
  \item
  \item
\end{itemize}

\newpage

>>>>

\begin{table}[t]\centering
  \caption{Comparison of telemetry designs}
  \label{t:telemetry-design}

@@

The Blackbox project similarly collects telemetry in broad strokes.
Every Java program submitted for compilation goes into the Blackbox database (minus
any comments above the main class) along with the compiler's response~\cite{bkmu-sigcse-2014}.
Though somewhat intrusive, the millions of programs in the Blackbox dataset
have enabled dozens of contributions to the area of CS
education~\cite{bask-icer-2018}, ranging from categorization of novice
errors~\cite{mk-fie-2014,m-masters-2016} to analyses of error frequency and
time-to-fix~\cite{ab-sigcse-2015}.

@@

\paragraph{Telemetry Enhancements: What and How to Sample}

One way to futher strengthen the privacy of any telemetry design, including
transparent telemetry, is to systematically add noise to the data using
techniques from differential
privacy~\cite{zhlbr-cc-2020,epk-ccs-2014,wblj-usenix-2017}.
Recent work that is especially relevant to the session-based data collected
by Roblox Studio shows how to add noise to traces~\cite{zhlbr-cc-2020},
how to account for known relationships between events~\cite{zhlbr-oopsla-2020},
and how to choose the noise amount on the client side~\cite{hlzbr-ecoop-2021}.
Applying differential privacy is subtle, however.
While we can likely fuzz the total number of type errors, if we were to
fuzz the number of \code{CodeTooComplex} errors, it might drastically
affect our conclusions.

Cooperative bug isolation is a method for designing
telemetry systems~\cite{liblit-thesis}.
The focus is not on privacy, but rather on how to collect a small amount of
data from each user and perform statistically-sound analyses.
Each feature of interest \emph{within} a user's codebase has a uniform-random
probability of contributing telemetry.
The system-builder can analyze this telemetry with predicates to identify
notable events and logistic regression to narrow down nondeterministic bugs.
There is a high burden on designers to decide what to capture,
but a careful design can minimize the data from each individual user.
%% more in diss: how to deal with native compilers, threads, dynamic loading
%% ... privacy is future work, can maybe avoid private data with a type system

Two further refinements, which reduce the burden on experts to
select points of interest, are adaptive bug isolation~\cite{nl-icse-2010}
and blame-proportional logging~\cite{lnsmc-usenix-2018}.
Adaptive bug isolation starts with a set of predicates, studies which are
most correlated with failures, and experiments with adding telemetry to nearby
predicates; this technique can reduce the overhead of telemetry by two orders
of magnitude relative to naive binary instrumentation.
Blame-proportional logging starts with lightweight telemetry to recognize
defects, assigns ranks to methods estimating their likelihood as root causes,
and uses the ranks and future observations to narrow down the cause.
Deep transfer learning is another promising way to automatically hone in on events of
interest~\cite{zfstt-ieeesensors-2022}.

%% \cite{fnm-sigmod-2020}
%% adaptive interventional debugging
%% failure -> correlated predicates -> temporal properties to overapprox relationships -> fault injection to discover true relationships

%% RAMSS workshop (remote measurement), sounds related but i haven't found proceedings
%% \cite{op-ramss-2003,op-ramss-2004}

\paragraph{User Studies: Errors and Type Errors}

Foundational:

\cite{wk-koli-2020,lgk-pj-2022,mcpcspss-abz-2020}
more edit sequences

Ballpark:

@@

bibliography of static type studies:
http://danluu.com/empirical-pl/

thomas kennedy .... generic usage monitoring ascilite 2003

ahmadzadeh elliman higgins iticse 2005

buffardi etal 2014 adaptive and social mechanisms

bddf-icse-2016
 sh edwards and jason snyder icer 2009 comparing effective and ineffective grading platform

murphy etal sigcse 2009 Retina: helping students

Choppella Haynes IU TR 426

Tip Dinesh tosem 2001

% ESP workshop on empirical studies of programming
% https://dl.acm.org/doi/proceedings/10.1145/266399
% nothing sounds big ... empirical yes, large no
% https://link.springer.com/content/pdf/10.1023/a:1008040416962.pdf

@@

%\newpage
%
%\appendix
%
%\section{Data Details}
%
%Tips for interpreting the data:
%
%\begin{itemize}
%  \item
%    Edit ranges are non-negative because we
%    implemented the interval arithmetic for them using unsigned integers.
%    To filter out negative edit ranges, we removed all ranges
%    greater than 4 billion.
%
%  \item
%  \item
%  \item
%\end{itemize}
%
%\newpage
